The Iterative Signature Algorithm for Gene Expression data

### 2009-08-06 eisa/inst/doc/EISA_tutorial.Rnw
eisa vignette: do not use Cairo package and add a VignetteEntry.

\documentclass{article}
\usepackage{ragged2e}
\usepackage{url}

@@

You can also use the \Rpackage{biclust} package to create image
plots, by calling the \Rfunction{drawHeatmap} function. The result is
in Fig.~\ref{fig:drawHeatmap}.
<<heatmap biclust pre,echo=FALSE,results=hide>>=
CairoPNG("heatmap.png", 400, 400 )
@ 
<<heatmap>>=
drawHeatmap(exprs(ALL[featureNames(modules),]), Bc, number=1) 
@
<<heatmap post,echo=FALSE,results=hide>>=
dev.off() 
@ 
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{heatmap}
  \caption{Heatmap of the first transcription module.}
  \label{fig:drawHeatmap}
\end{figure}

@@

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
CairoPNG("parallel.png", 400, 400 )
@ 
<<parallel>>=
profile.plot(modules, 2, ALL, plot="both")
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{parallel}
\caption{Profile plots for the second bicluster found by ISA.}
\label{fig:parallel}
\end{figure}

>>>>

% \VignetteIndexEntry{The Iterative Signature Algorithm for Gene Expression Data}
\documentclass{article}
\usepackage{ragged2e}
\usepackage{url}

@@

You can also use the \Rpackage{biclust} package to create image
plots, by calling the \Rfunction{drawHeatmap} function. The result is
in Fig.~\ref{fig:drawHeatmap}.
<<heatmap biclust pre,echo=FALSE,results=hide>>=
png("heatmap.png", 400, 400 )
@ 
<<heatmap>>=
drawHeatmap(exprs(ALL[featureNames(modules),]), Bc, number=1) 
@
<<heatmap post,echo=FALSE,results=hide>>=
dev.off() 
@ 
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{heatmap}
  \caption{Heatmap of the first transcription module.}
  \label{fig:drawHeatmap}
\end{figure}

@@

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
png("parallel.png", 400, 400 )
@ 
<<parallel>>=
profile.plot(modules, 2, ALL, plot="both")
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{parallel}
\caption{Profile plots for the second bicluster found by ISA.}
\label{fig:parallel}
\end{figure}
